---
title: "DataCamp Depth Track"
author: "Your Name"
date: 'Last compiled: `r format(Sys.time(), "%b %d, %Y")`'
output: ioslides_presentation
---

```{r setup, include=FALSE, warning = FALSE, message = FALSE}
library(tidyverse)
knitr::opts_chunk$set(echo = FALSE)

```

## DataCamp Depth Track

* Each slide is started with two hashes (`##`)

* To read more about ioslides click [here](https://bookdown.org/yihui/rmarkdown/ioslides-presentation.html)


## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3
- Bullet 4

## Slide with R Output

```{r label = "cars", echo = TRUE, comment = NA}
summary(cars)
```

## Slide with Plot

```{r label = "pressure", fig.cap = "Something interesting goes here"}
ggplot(data = pressure, aes(y = pressure, x = temperature)) +
  geom_point() +
  theme_bw()
```

